Cross-lingual Document Similarity and Event Detection \todo{Better title...}

### 2015-03-06 rupnik2015.tex
- added story linking evaluation

>>>>

\begin{table}[h]
\caption{Accuracy of story linking with different sets of features}
\label{table:linkingEval}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Features & CA & Precision & Recall \\ \cline{1-4}
  CCA & 73.2\% & 0.717 & 0.763 \\ \cline{1-4}
  Concepts & 88.5\% & 0.888 & 0.882 \\ \cline{1-4}
  Misc & 62.7\% & 0.583 & 0.904 \\ \cline{1-4}
  CCA + concepts & 89.0\% & 0.893 & 0.887 \\ \cline{1-4}
  All & 88.9\% & 0.893 & 0.884 \\ \cline{1-4}
  \hline
\end{tabular}
\end{center}
\end{table}
